High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-09-13 notebooks/tables.Rmd
mostly doen

# Logic:
tab_i <- tab_i[variable %in% measures]
tab_i <- tab_i[source == chosen_source]
tab_i <- tab_i[dataname %in% chosen_data]
tab_i[,dataname:=factor(dataname,levels=chosen_data)]
tab_i <- dcast(tab_i, model + generator ~ dataname + variable)
col_names <- c(
  "Model",
  "Generator",
  rep(measure_names,length(chosen_data))
)
caption <- sprintf(
  "Results for %s datasets: sample averages +/- one standard deviation across counterfactuals. Best outcomes are highlighted in bold. Asterisks indicate that the given value is more than one (*) or two (**) standard deviations away from the baseline (Wachter). \\label{tab:results-%s} \\newline",
  chosen_source,
  chosen_source
)
file_name <- sprintf(
  "paper/contents/table-%s.tex",
  chosen_source
)
sub_header <- rep(length(measures), length(chosen_data))
names(sub_header) <- chosen_data
header <- c(
  " " = 2, sub_header
)
line_sep <- c(rep("",length(measures)-1),"\\addlinespace")
algin_cols <- c(rep('l',2),rep('c',ncol(tab_i)-2))
kbl(
  tab_i, caption = caption, 
  align = algin_cols, col.names=col_names, booktabs = T, escape=F, 
  format="latex", linesep = line_sep 
) %>%
  kable_styling(latex_options = c("scale_down")) %>%
  kable_paper(full_width = F) %>%
  add_header_above(header) %>%
  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
  save_kable(file_name)
```

@@

```{r}
tab_full <- dcast(tab, dataname + model + generator ~ variable)
col_names <- c(
  "Model",
  "Data",
  "Generator",
  "Cost ↓", 
  "Unfaithfulness ↓", 
  "Implausibility ↓", 
  "Redundancy ↑",
  "Uncertainty ↓",
  "Validity ↑"
)
algin_cols <- c(rep('l',3),rep('c',ncol(tab_full)-3))
kbl(
  tab_full, caption = "All results for all datasets: sample averages +/- one standard deviation over all counterfactuals. Best outcomes are highlighted in bold. Asterisks indicate that the given value is more than one (*) or two (**) standard deviations away from the baseline (Wachter). \\label{tab:results-full} \\newline", 
  align = "c", col.names=col_names, booktabs = T, escape=F, 
  format="latex"
) %>%
  kable_styling(latex_options = c("scale_down")) %>%
  kable_paper(full_width = F) %>%
  collapse_rows(columns = 1:3, latex_hline = "custom", valign = "top", custom_latex_hline = 1:2) %>%
  save_kable("paper/contents/table_all.tex")
```

@@

```{r}
tab_full <- dcast(tab_valid, dataname + model + generator ~ variable)
col_names <- c(
  "Model",
  "Data",
  "Generator",
  "Cost ↓", 
  "Unfaithfulness ↓", 
  "Implausibility ↓", 
  "Redundancy ↑",
  "Uncertainty ↓",
  "Validity ↑"
)
algin_cols <- c(rep('l',3),rep('c',ncol(tab_full)-3))
kbl(
  tab_full, caption = "All results for all datasets: sample averages +/- one standard deviation over all valid counterfactuals. Best outcomes are highlighted in bold. Asterisks indicate that the given value is more than one (*) or two (**) standard deviations away from the baseline (Wachter). \\label{tab:results-full-valid} \\newline", 
  align = "c", col.names=col_names, booktabs = T, escape=F, 
  format="latex"
) %>%
  kable_styling(latex_options = c("scale_down")) %>%
  kable_paper(full_width = F) %>%
  collapse_rows(columns = 1:3, latex_hline = "custom", valign = "top", custom_latex_hline = 1:2) %>%
  save_kable("paper/contents/table_all_valid.tex")
```

@@

```{r}
files <- list.files("artifacts/params/")
dt <- lapply(files[grepl(".csv", files)], function(x) {
    fread(file.path("artifacts/params/", x))
})
dt <- Reduce(function(x,y) {rbind(x,y, fill=TRUE)}, dt)
setcolorder(
  dt, 
  c(
    "dataname", "n_obs",
    "n_hidden", "n_layers", "activation", "n_ens",
    "epochs", "batch_size",
    "jem_sampling_steps", "sgld_batch_size", "lambda"
  )
)
dt[,dataname:=factor(dataname, levels=c("Linearly Separable", "Moons", "Circles", "MNIST", "GMSC"))]
dt <- dt[order(dataname)]
dt_ebm <- dt[,.(dataname, jem_sampling_steps, sgld_batch_size, lambda)]
col_names <- c(
  "Dataset",
  "SGLD Steps", "Batch Size", "$\\lambda$"
)
kbl(
  dt_ebm, caption = "EBM hyperparemeter choices for our experiments. \\label{tab:ebmparams} \\newline", 
  align = "r", col.names=col_names, booktabs = T, escape=F, 
  format="latex"
) %>%
  kable_styling(font_size = 8) %>%
  kable_paper(full_width = F) %>%
  save_kable("paper/contents/table_ebm_params.tex")
```

@@

```{r}
dt_exp <- dt[,.(dataname, n_obs, n_hidden, n_layers, activation, n_ens, epochs, batch_size)]
col_names <- c(
  "Dataset", "Sample Size",
  "Hidden Units", "Hidden Layers", "Activation", "Ensemble Size",
  "Epochs", "Batch Size"
)
header <- c(" " = 2, "Network Architecture" = 4, "Training" = 2)
kbl(
  dt_exp, caption = "Paremeter choices for our experiments. \\label{tab:params} \\newline", 
  align = "r", col.names=col_names, booktabs = T, escape=F, 
  format="latex"
) %>%
  kable_styling(latex_options = c("scale_down")) %>%
  kable_paper(full_width = F) %>%
  add_header_above(header) %>%
  save_kable("paper/contents/table_params.tex")
```

```{r}
files <- list.files("artifacts/params/generator")
dt <- lapply(files, function(x) {
    fread(file.path("artifacts/params/generator", x))
})
dt <- Reduce(function(x,y) {rbind(x,y, fill=TRUE)}, dt)
dt <- dt[,.(dataname,eta,λ1,λ3,λ3)]
dt[,dataname:=factor(dataname, levels=c("Linearly Separable", "Moons", "Circles", "MNIST", "GMSC"))]
dt <- dt[order(dataname)]
col_names <- c(
  "Dataset",
  "$\\eta$", "$\\lambda_1$", "$\\lambda_2$", "$\\lambda_3$"
)
kbl(
  dt, caption = "Generator hyperparameters. \\label{tab:genparams} \\newline", 
  align = "r", col.names=col_names, booktabs = T, escape=F, 
  format="latex"
) %>%
  kable_styling(font_size = 8) %>%
  kable_paper(full_width = F) %>%
  save_kable("paper/contents/table_gen_params.tex")
```

```{r}
files <- list.files("artifacts/results/")
dt <- lapply(files[grepl("_model_performance.csv", files)], function(x) {
    fread(file.path("artifacts/results/", x))
})
dt <- Reduce(function(x,y) {rbind(x,y, fill=TRUE)}, dt)
dt[,dataname:=factor(dataname, levels=c("Linearly Separable", "Moons", "Circles", "MNIST", "GMSC"))]
dt <- dt[order(dataname,mod_name)]
setcolorder(
  dt, 
  c(
    "dataname", "mod_name",
    "acc", "precision", "f1score"
  )
)
col_names <- c("Dataset", "Model", "Accuracy", "Precision", "F1-Score")
kbl(
  dt, caption = "Various standard performance metrics for our different models grouped by dataset. \\label{tab:perf} \\newline", 
  align = "r", col.names=col_names, booktabs = T, escape=F, 
  format="latex", digits=2
) %>%
  kable_styling(font_size = 8) %>%
  kable_paper(full_width = F) %>%
  add_header_above(c(" "=2, "Performance Metrics" = 3)) %>%
  collapse_rows(columns = 1, latex_hline = "custom", valign = "top", custom_latex_hline = 1) %>%
  save_kable("paper/contents/table_perf.tex")
```

>>>>

# Logic:
tab_i <- tab_i[variable %in% measures]
tab_i <- tab_i[source == chosen_source]
tab_i <- tab_i[dataname %in% chosen_data]
tab_i[,dataname:=factor(dataname,levels=chosen_data)]
tab_i <- dcast(tab_i, model + generator ~ dataname + variable)
col_names <- c(
  "Model",
  "Generator",
  rep(measure_names,length(chosen_data))
)
caption <- sprintf(
  "Results for %s datasets: sample averages +/- one standard deviation across counterfactuals. Best outcomes are highlighted in bold. Asterisks indicate that the given value is more than one (*) or two (**) standard deviations away from the baseline (Wachter). \\label{tab:results-%s} \\newline",
  chosen_source,
  chosen_source
)
file_name <- sprintf(
  "paper/contents/table-%s.tex",
  chosen_source
)
sub_header <- rep(length(measures), length(chosen_data))
names(sub_header) <- chosen_data
header <- c(
  " " = 2, sub_header
)
line_sep <- c(rep("",length(measures)-1),"\\addlinespace")
algin_cols <- c(rep('l',2),rep('c',ncol(tab_i)-2))
kbl(
  tab_i, caption = caption, 
  align = algin_cols, col.names=col_names, booktabs = T, escape=F, 
  format="latex", linesep = line_sep 
) %>%
  kable_styling(latex_options = c("scale_down")) %>%
  kable_paper(full_width = T) %>%
  add_header_above(header) %>%
  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
  save_kable(file_name)
```

@@

```{r}
tab_full <- dcast(tab, dataname + model + generator ~ variable)
col_names <- c(
  "Model",
  "Data",
  "Generator",
  "Cost ↓", 
  "Unfaithfulness ↓", 
  "Implausibility ↓", 
  "Redundancy ↑",
  "Uncertainty ↓",
  "Validity ↑"
)
algin_cols <- c(rep('l',3),rep('c',ncol(tab_full)-3))
kbl(
  tab_full, caption = "All results for all datasets: sample averages +/- one standard deviation over all counterfactuals. Best outcomes are highlighted in bold. Asterisks indicate that the given value is more than one (*) or two (**) standard deviations away from the baseline (Wachter). \\label{tab:results-full} \\newline", 
  align = "c", col.names=col_names, booktabs = T, escape=F, 
  format="latex"
) %>%
  kable_styling(latex_options = c("scale_down")) %>%
  kable_paper(full_width = T) %>%
  collapse_rows(columns = 1:3, latex_hline = "custom", valign = "top", custom_latex_hline = 1:2) %>%
  save_kable("paper/contents/table_all.tex")
```

@@

```{r}
tab_full <- dcast(tab_valid, dataname + model + generator ~ variable)
col_names <- c(
  "Model",
  "Data",
  "Generator",
  "Cost ↓", 
  "Unfaithfulness ↓", 
  "Implausibility ↓", 
  "Redundancy ↑",
  "Uncertainty ↓",
  "Validity ↑"
)
algin_cols <- c(rep('l',3),rep('c',ncol(tab_full)-3))
kbl(
  tab_full, caption = "All results for all datasets: sample averages +/- one standard deviation over all valid counterfactuals. Best outcomes are highlighted in bold. Asterisks indicate that the given value is more than one (*) or two (**) standard deviations away from the baseline (Wachter). \\label{tab:results-full-valid} \\newline", 
  align = "c", col.names=col_names, booktabs = T, escape=F, 
  format="latex"
) %>%
  kable_styling(latex_options = c("scale_down")) %>%
  kable_paper(full_width = T) %>%
  collapse_rows(columns = 1:3, latex_hline = "custom", valign = "top", custom_latex_hline = 1:2) %>%
  save_kable("paper/contents/table_all_valid.tex")
```

@@

```{r}
files <- list.files("artifacts/params/")
dt <- lapply(files[grepl(".csv", files)], function(x) {
    fread(file.path("artifacts/params/", x))
})
dt <- Reduce(function(x,y) {rbind(x,y, fill=TRUE)}, dt)
setcolorder(
  dt, 
  c(
    "dataname", "n_obs",
    "n_hidden", "n_layers", "activation", "n_ens",
    "epochs", "batch_size",
    "jem_sampling_steps", "sgld_batch_size", "lambda"
  )
)
dt[,dataname:=factor(dataname, levels=c("Linearly Separable", "Moons", "Circles", "MNIST", "GMSC"))]
dt <- dt[order(dataname)]
dt_ebm <- dt[,.(dataname, jem_sampling_steps, sgld_batch_size, lambda)]
col_names <- c(
  "Dataset",
  "SGLD Steps", "Batch Size", "$\\lambda$"
)
kbl(
  dt_ebm, caption = "EBM hyperparemeter choices for our experiments. \\label{tab:ebmparams} \\newline", 
  align = "r", col.names=col_names, booktabs = T, escape=F, 
  format="latex"
) %>%
  kable_styling(font_size = 8) %>%
  kable_paper(full_width = T) %>%
  save_kable("paper/contents/table_ebm_params.tex")
```

@@

```{r}
dt_exp <- dt[,.(dataname, n_obs, n_hidden, n_layers, activation, n_ens, epochs, batch_size)]
col_names <- c(
  "Dataset", "Sample Size",
  "Hidden Units", "Hidden Layers", "Activation", "Ensemble Size",
  "Epochs", "Batch Size"
)
header <- c(" " = 2, "Network Architecture" = 4, "Training" = 2)
kbl(
  dt_exp, caption = "Paremeter choices for our experiments. \\label{tab:params} \\newline", 
  align = "r", col.names=col_names, booktabs = T, escape=F, 
  format="latex"
) %>%
  kable_styling(latex_options = c("scale_down")) %>%
  kable_paper(full_width = T) %>%
  add_header_above(header) %>%
  save_kable("paper/contents/table_params.tex")
```

```{r}
files <- list.files("artifacts/params/generator")
dt <- lapply(files, function(x) {
    fread(file.path("artifacts/params/generator", x))
})
dt <- Reduce(function(x,y) {rbind(x,y, fill=TRUE)}, dt)
dt <- dt[,.(dataname,eta,λ1,λ3,λ3)]
dt[,dataname:=factor(dataname, levels=c("Linearly Separable", "Moons", "Circles", "MNIST", "GMSC"))]
dt <- dt[order(dataname)]
col_names <- c(
  "Dataset",
  "$\\eta$", "$\\lambda_1$", "$\\lambda_2$", "$\\lambda_3$"
)
kbl(
  dt, caption = "Generator hyperparameters. \\label{tab:genparams} \\newline", 
  align = "r", col.names=col_names, booktabs = T, escape=F, 
  format="latex"
) %>%
  kable_styling(font_size = 8) %>%
  kable_paper(full_width = T) %>%
  save_kable("paper/contents/table_gen_params.tex")
```

```{r}
files <- list.files("artifacts/results/")
dt <- lapply(files[grepl("_model_performance.csv", files)], function(x) {
    fread(file.path("artifacts/results/", x))
})
dt <- Reduce(function(x,y) {rbind(x,y, fill=TRUE)}, dt)
dt[,dataname:=factor(dataname, levels=c("Linearly Separable", "Moons", "Circles", "MNIST", "GMSC"))]
dt <- dt[order(dataname,mod_name)]
setcolorder(
  dt, 
  c(
    "dataname", "mod_name",
    "acc", "precision", "f1score"
  )
)
col_names <- c("Dataset", "Model", "Accuracy", "Precision", "F1-Score")
kbl(
  dt, caption = "Various standard performance metrics for our different models grouped by dataset. \\label{tab:perf} \\newline", 
  align = "r", col.names=col_names, booktabs = T, escape=F, 
  format="latex", digits=2
) %>%
  kable_styling(font_size = 8) %>%
  kable_paper(full_width = T) %>%
  add_header_above(c(" "=2, "Performance Metrics" = 3)) %>%
  collapse_rows(columns = 1, latex_hline = "custom", valign = "top", custom_latex_hline = 1) %>%
  save_kable("paper/contents/table_perf.tex")
```
